### 2019-06-04 fe_px_paper/fe_body_text.tex
Incorporated Lee's 1st-round comments through Section 1

The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives\,\cite{Mulford2005,Muller2014}.
While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
% 
% 
% 
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue\,\cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose\,\cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
% Change up the next sentance a bit
% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
%\,\cite{Qaim201731}. 
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}. 
As part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out in a  thin-foil stacked-target experiment, using proton irradiation of natural iron foils with titanium and copper monitor foils.
While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.

Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element that is biologically relevant and essential in trace quantities. 
Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection\,\cite{Dong2015}.
Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}. 
\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies\,\cite{Wang2017}.
\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications\,\cite{Wang2017}.

@@

While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region\,\cite{PhysRevC.73.034613,PhysRevC.45.1171}.
These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes. 
In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.

@@

A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
One stack covers the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.

>>>>

The next generation of nuclear medicine 
% would appear to be based upon 
is likely to involve the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
% The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  
These make possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives, and informing researchers in their quest to develop new treatments\,\cite{Mulford2005,Muller2014}.
While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
% 
% 
% 
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue\,\cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose\,\cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
% Change up the next sentance a bit
% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
%\,\cite{Qaim201731}. 
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
One particular group of  emerging radionuclides are 
% the various 
positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.

However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies \cite{voinov, tavukcu}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out 
% in a
using the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
natural iron foils with titanium and copper monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work seeks to complement 
% these measurements 
earlier measurements at 40--100\,MeV proton beam energies and extend them down to reaction thresholds, in order to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

Manganese radionuclides are desirable for radiopharmaceutical applications, as 
% manganese is a 
the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection\,\cite{Dong2015}.
% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging\,\cite{Dong2015}.  . 
Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long lifetime and unfavorable high-energy decay gamma-rays 
% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
make it undesirable for clinical applications.
% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min)
% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
% Another emerging manganese radionuclide is 
In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), 
% whose short lifetime makes it 
is more clinically suitable for rapid metabolic studies\,\cite{Wang2017}.
% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
% In addition, 
\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging,\cite{Wang2017}.

@@

% While these efforts have been motivated by the production cross section of the
In addition to their interest for PET studies, the \ce{^{51,52g,52m}Mn} excitation functions 
% radionuclides for PET studies, this experiment 
offer an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region\,\cite{PhysRevC.73.034613,PhysRevC.45.1171}.
These measurements also provide an opportunity to benchmark 
% a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve 
the predictive capabilities of  reaction modeling codes used for nuclear reaction evaluations and the way in which they implement the underlying physical reaction mechanisms.  
% codes. 
% In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.

@@

A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
One stack covered the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.
